---
title: "R Notebook"
output: html_notebook
---

# Theory
The conditional quantile regression estimator by Koenker and Basset (1978) for the $\tau$-th quantile is defined as
 
$$
\widehat{\beta}_{QR} = \min_{b} \sum^{n}_{i=1} \rho_\tau (y_i - X'_i b_\tau)
$$

where $\rho_\tau = u_i\cdot (\tau - 1(u_i<0))$ is a re-weighting function (called "check"-function) of the residuals $u$_i.

# Basic settings 

We will use `quantreg` package so we need to install it. 

```{r}
library(quantreg)
```

Now, we will read the data.


```{r}
rema <- read.csv2('../data-raw/project_data_train.csv', 
                 header = T, 
                 stringsAsFactors = F, 
                 dec = '.')
rema <- subset(rema, pzn_district != '' &  !is.na(trans_dwelling_rooms) & !is.na(trans_dwelling_floor_area))
rema$year <- format(as.Date(rema$trans_date,'%Y-%m-%d'),'%Y')
rema$year <- as.numeric(as.factor(rema$year))
rema$rooms <- ifelse(rema$trans_dwelling_rooms >=4,4,rema$trans_dwelling_rooms)
rema$rooms <- as.factor(rema$rooms)
rema$pzn_district <- as.factor(rema$pzn_district)
rema$floor_area_centr <- scale(rema$trans_dwelling_floor_area, center = T, scale = F)
rema
```

```{r}
summary(rema)
```



```{r}
model <- rq(formula = trans_dwelling_price ~ year + floor_area_centr + 
                I(floor_area_centr^2) +  rooms + pzn_district,
            tau = c(0.1,0.25,0.5,0.75,0.9),
            data = rema,
            method = 'fn')
summary(model)
```

```{r}
coef(model)
```

```{r}
plot(summary(model))
```

```{r}
anova(model)
```

$$
R_1(\tau) = 1 - \frac{\sum_{y_i \ge \hat y_i} \tau \cdot \vert y_i-\hat y_i \vert +\sum_{y_i<\hat y_i} (1-\tau) \cdot \vert y_i-\hat y_i \vert}{\sum_{y_i \ge \bar y} \tau \cdot \vert y_i-\bar y \vert +\sum_{y_i<\bar y_i} (1-\tau) \cdot \vert y_i-\bar y \vert},
$$

where $\hat y_i =\alpha_{\tau}+\beta_{\tau}x$ is the fitted $\tau$th quantile for observation $i$ and $\bar{y}=\beta_{\tau}$ is the fitted value from the intercept-only model.

```{r}
model0 <- rq(formula = trans_dwelling_price ~ 1,
            tau = c(0.1,0.25,0.5,0.75,0.9),
            data = rema,
            method = 'fn')
```

```{r}
rho <- function(u,tau=.5) u*(tau - (u < 0))
1 - model$rho/model0$rho
```



# Bibliograhy

Koenker, R., & Bassett, G. (1978) "Regression Quantiles", Econometrica, Vol. 46(1), pp. 33-50


