---
title: "Regression and outliers"
output: html_notebook
---

# Load packages

```{r}
library(dplyr)
library(extremevalues)
library(lmtest)
```


# Read the data

```{r}
rema <- read.csv2('../data-raw/project_data_train.csv', 
                 header = T, 
                 stringsAsFactors = F, 
                 dec = '.')
rema
```


```{r}
plot(rema$trans_dwelling_price, rema$trans_dwelling_floor_area)
plot(log(rema$trans_dwelling_price), rema$trans_dwelling_floor_area)
plot(log(rema$trans_dwelling_price), log(rema$trans_dwelling_floor_area))
```

## Testing regression assumptions

```{r}
m1 <- lm(trans_dwelling_price ~ trans_dwelling_floor_area, data= rema)
summary(m1)
plot(m1)
```

```{r}
m1_measures <- influence.measures(m1)
str(m1_measures,1)
head(m1_measures$infmat)
```


### the Breusch-Pagan test against heteroskedasticity.

```{r}
lmtest::bptest(m1)
```


### Rainbow test for linearity.

```{r}
lmtest::raintest(trans_dwelling_price ~ trans_dwelling_floor_area, 
                 data = rema,
                 order.by = ~trans_dwelling_floor_area)
```

### RESET test 

Another appropriate procedure is the RESET test, which tests whether some auxiliary variables improve the fit significantly. 

```{r}
lmtest::resettest(trans_dwelling_price ~ trans_dwelling_floor_area,
                  data = rema,
                  power = 2,
                  type = "regressor")
```

```{r}
lmtest::raintest(trans_dwelling_price ~ trans_dwelling_floor_area,
                  order.by = ~trans_dwelling_floor_area,
                  data = rema)
lmtest::raintest(trans_dwelling_price ~ trans_dwelling_floor_area + I(trans_dwelling_floor_area^2),
                 order.by = ~trans_dwelling_floor_area,
                data = rema)
```

## Test for outliers (based on rstudent)

Reports the Bonferroni p-values for Studentized residuals in linear and generalized linear models, based on a t-test for linear models and normal-distribution test for generalized linear models.


```{r}
outlierTest(m1, n.max = Inf) ## all outliers 
```

